### 2010-12-14 Text/paper.tex
Added another patch from Michal. Started obtaining Asymmetric cap region. Pushing the continuous interface to the limit. The Poiseuille profile just doesn't work in this case. Let us see results.

\section{Non-axisymmetric case}
That could be fucking difficult. For example according to \cite{heil-threedim} for the capillary
number $Ca=0.01$, the radiuses converge as $r_h=0.99$ and $r_d=1.1$. Therefore one needs to resolve
as the $0.5\%$ of whole channel width to see the difference. That certainly implies so large grid
that can kill the simulation at least $200x200x3000$. However, we can refer to artificially made
interface as $1-2$ lattice Boltzmann units but keeping the capillary number as it is required. In
this case we can refer like we can't resolve the interface but we can certainly to attribute it to
the wall gradient as extreme case. The dimnesionalization case is therefore as follows:
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma},
\end{equation}
therefore let us pick up the same parameters as for the previous case and just change use the
pressure gradient reduced by $1000$ as $Ca=10$ and $Ca=0.01$ are different. 
Let us wait for simulation.

\section{Capillary number region}

\section{Simulation setup}

>>>>

\section{Non-axisymmetric case}
That could be fucking difficult. For example according to \cite{heil-threedim} for the capillary
number $Ca=0.01$, the radiuses converge as $r_h=0.99$ and $r_d=1.1$. Therefore one needs to resolve
as the $0.5\%$ of whole channel width to see the difference. That certainly implies so large grid
that can kill the simulation at least $200x200x3000$. However, we can refer to artificially made
interface as $1-2$ lattice Boltzmann units but keeping the capillary number as it is required. In
this case we can refer like we can't resolve the interface but we can certainly to attribute it to
the wall gradient as extreme case. The dimnesionalization case is therefore as follows:
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma},
\end{equation}
therefore let us pick up the same parameters as for the previous case. To perform simulations we
started with the following parameters as
$k=0.04$,$A=0.04$,$\Gamma=1.0$,$N_x\mathrm{x}N_y\mathrm{x}N_z=52\mathrm{x}52\mathrm{x}750$.The
initialized density was chosen as $w=2.5$ lattice Boltzmann units. For underresolved schemes, the
pressure gradient doesn't work in the way we expect. Therefore, we take pressure gradient in the
following way and later on establish the associated capillary number. In this case we can check the
extreme values for the pressure gradients and the continuous interface methods:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=
\begin{cases}
1\dots10\mathrm{x}10^{-6}\\
10,15\dots 100 \mathrm{x}10^{-6}
\end{cases}
\end{equation}

\section{Capillary number region}
The same as in the previous example can help us to identify the necessary capillary regime. The
most important thing is to establish different accentricity factors.
\section{Simulation setup}
